### 2017-05-08 relatedwork.tex
ok to ship

The most closely related work is that of Chen et. al \cite{PLDI13}.  We use two of the same compiler data sets, and both apply the FPF \cite{Gonzalez} algorithm.  The distance metrics used with FPF in the previous work, however, were \emph{ad hoc}, chosen for each program by hand, produced poorer results for the critical portion of the curve for the two hard data sets, and were not extended to provide any fault localization.  This paper uses the FPF approach in the context of a more principled causal comparison of program executions that applies in theory to any executions, not just failing test cases, and introduces novel fault localizations.  Prior to the FPF-based work, Francis et al. \cite{Podgurski04}, Podgurski et al. \cite{Podgurski03} and others \cite{Liu06,Liblit05} used clustering to attempt to solve similar problems in identifying distinct faults, on simpler human-generated data sets.  Chen et. al \cite{PLDI13} provide an in-depth comparison of clustering and ranking, and the advantages of ranking (as well as some possible limitations).  Jones et al. discuss general issues in debugging multiple faults efficiently \cite{Jones07}.

Fault localization \cite{FaultSurvey,NearNeighbor,Liblit03,Liblit05,Cleve05,Jones2002,Jones05,Jones07,GroceError,ChakiLev,Liu06,SPIN03,Santelices:ICSE:2009,Abreu:2006:PRDC,xuan2014test,DD}, even specifically for compilers \cite{Whalley94}, is a long-standing field of research.  Recently, fault localization researchers have used program mutants to improve statistical \cite{Jones2002} fault localization techniques \cite{MUSE,DebroyMutant,FasterMutant,multilingual,Metallaxis,Papadakis}.
%The core of this work has been the belief that faulty program locations are (1) more likely to change a failing test to successful when mutated and (2) less likely to change a successful test case to faulty when mutated.  This clearly connects to our general notion that how two test cases respond to a set of mutants is a good measure of their semantic similarity.
The work of Hong et al. \cite{multilingual} on MUSEUM and Moon et al. \cite{MUSE} on MUSE provides a good summary of other work along these lines. \comment{, and is perhaps most similar to ours in assumptions, in particular ``Conjecture 1'' that a test case that used to fail on a program is more likely to pass on a mutation of a faulty statement.  While we suggest some localizations as a welcome and interesting side effect of our distance metric and FPF analysis, our primary goal is the discovery of all faults.} Much fault localization work is largely (in many cases exclusively) based on single-fault scenarios; e.g., the MUSE \cite{MUSE} evaluation includes only 2 of 14 scenarios with multiple faults, and those scenarios include only a few faults.   The statistical approaches may owe some of their superiority in experiments over other methods to the use of mostly single-fault evaluations \cite{Jones05}.  By focusing on a single failing test case (for us, selected by fuzzer taming) as the locus of analysis, our work, like some early efforts \cite{NearNeighbor,Cleve05,GroceError} may be more suited for situations involving many faults.  MUSEUM \cite{multilingual} also revisits this approach, combining the MUSE formula with localization using only a single failure.

>>>>

The most closely related work is that of Chen et. al \cite{PLDI13}.  We use two of the same compiler data sets, and both apply the FPF \cite{Gonzalez} algorithm.  The distance metrics used with FPF in the previous work, however, were \emph{ad hoc}, chosen for each program by hand, produced poorer results for the critical portion of the curve for the two hard data sets, and were not extended to provide any fault localization.  This paper uses the FPF approach in the context of a more causal comparison of program executions that applies in theory to any executions, not just failing test cases, and introduces a novel fault localization.  Prior to the FPF-based work, Francis et al. \cite{Podgurski04}, Podgurski et al. \cite{Podgurski03} and others \cite{Liu06,Liblit05} used clustering to attempt to solve similar problems in identifying distinct faults, on simpler human-generated data sets.  Chen et. al \cite{PLDI13} provide an in-depth comparison of clustering and ranking, and the advantages of ranking (as well as some possible limitations).  Jones et al. discuss general issues in debugging multiple faults efficiently \cite{Jones07}.  The work of Groce et al. \cite{OneTest} provides an alternative approach to fault identification, based on term rewriting to normalize failures.  However, this approach is not currently applicable to compiler fuzzing, as it only support tests that are sequences of method calls.

Fault localization \cite{FaultSurvey,NearNeighbor,Liblit03,Liblit05,Cleve05,Jones2002,Jones05,Jones07,GroceError,ChakiLev,Liu06,SPIN03,Santelices:ICSE:2009,Abreu:2006:PRDC,xuan2014test,DD}, even specifically for compilers \cite{Whalley94}, is a long-standing field of research.  Recently, fault localization researchers have used program mutants to improve statistical \cite{Jones2002} fault localization techniques \cite{MUSE,DebroyMutant,FasterMutant,multilingual,Metallaxis,Papadakis}.
%The core of this work has been the belief that faulty program locations are (1) more likely to change a failing test to successful when mutated and (2) less likely to change a successful test case to faulty when mutated.  This clearly connects to our general notion that how two test cases respond to a set of mutants is a good measure of their semantic similarity.
The work of Hong et al. \cite{multilingual} on MUSEUM and Moon et al. \cite{MUSE} on MUSE provides a good summary of other work along these lines. \comment{, and is perhaps most similar to ours in assumptions, in particular ``Conjecture 1'' that a test case that used to fail on a program is more likely to pass on a mutation of a faulty statement.  While we suggest some localizations as a welcome and interesting side effect of our distance metric and FPF analysis, our primary goal is the discovery of all faults.} Much fault localization work is largely (in many cases exclusively) based on single-fault scenarios; e.g., the MUSE \cite{MUSE} evaluation includes only 2 of 14 scenarios with multiple faults, and those scenarios include only a few faults.   The statistical approaches may owe some of their superiority in experiments over other methods to the use of mostly single-fault evaluations \cite{Jones05}.  By focusing on a single failing test case (for us, selected by fuzzer taming) as the locus of analysis, our work, like some early efforts \cite{NearNeighbor,Cleve05,GroceError} may be more suited for situations involving many faults.  \comment{MUSEUM \cite{multilingual} also revisits this approach, combining the MUSE formula with localization using only a single failure. }
